### 2022-09-27 NSF2022/Description/broaderimpacts.tex

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic particles. The simulations use a new, yet
intuitive, approach that accounts for important and complex systems
that are presently out of reach in computational material science. These complex
systems include optimal shape design in metamaterials and
fusion and fission of amphiphilic bilayer membranes. The further
development to three-dimensional models describing colloidal systems could be
transformative in biomedicine and material science. The research draws
from expertise in scientific computing, physics of fluids, and
mathematics. The mathematical component incorporates leading
variational techniques and offers insight into fundamentals of material
science. The project brings socially consequential research into the
classroom, and offers undergraduates the opportunity to train alongside
faculty and postdoctoral fellows. With its combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the importance of mathematics and computation to all areas of
science and engineering.
%The proposed mathematical analysis, modeling, and numerical algorithms
%will transform our understanding of the collective dynamics of
%amphiphilic particles such as (1) their self-assembly into micelles and
%bilayers, (2) the material properties of such self-assembly, and (3) the
%interaction between these building blocks. In addition to biophysical
%applications, amphiphilic Janus particles have recent popularity in the
%fabrication of smart materials. The proposed work will have a
%transformative impact on precision design for specific mechanical
%properties of materials made of amphiphilic nanoparticles. An important
%component of this proposal is the interdisciplinary education and
%training of both undergraduate students, graduate students, and
%postdoctoral fellows. The combination of mathematical modeling,
%analysis, and scientific computing in this project provides a compelling
%example of the importance of mathematics and computation in biophysics
%and engineering applications. The concepts and methods described here go
%beyond the context of amphiphilic particles and lipid molecules. They
%extend to other problems featuring microscopic phase separation that
%leads to formation of mesoscopic domains. This situation arises, for
%example, in biological development in systems biology. The methods
%developed here have the potential to impact those and other related
%areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
%The topics of this proposal have application in robotics, machine
%learning, and engineering.
To foster training in mathematical sciences,
the proposal supports one undergraduate researcher (UR) per year
from the lead institution.
PI RR has worked side-by-side and
published with undergraduate coauthors in
\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}.
He is presently mentoring a Clare Boothe Luce Scholar 
on mathematical analysis of trends in election redistricting.
With another Fordham supported UR,
he is finishing a paper on a closed-form 
energy density for translationally invariant bilayers. 
Based on these experiences, we have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep]
%\noitemsep
\item Translate project code from MATLAB into a compiled language

@@

\end{enumerate}
The UR support is for eight summer weeks. 
In addition to collaborating with the PI,
they will have tutorials and receive training in
mathematical writing and presentation.
The UR will have a desk and meeting room
in a recently completed collaboration space
built for the Mathematics Department. 
As a condition of support, 
they will be required to write a summary report and
give a presentation in the university's undergraduate
research symposium.  The PI 
will encourage the
UR to participate in a national conference.

@@

To maximize vertical integration, the PIs and personnel
will travel to New York for one or two weeks during the summers.
Finally, we will create several modules to include in our courses. These
modules will introduce topics from numerical linear algebra and
optimization, and highlight concrete applications of mathematics
based on the ideas of the proposal.
%The proposed research will have an immediate impact on undergraduate and
%graduate education. At the undergraduate level, the project will include
%and support undergraduate researchers from Fordham University. The
%supported summer researchers will gain valuable first-hand
%interdisciplinary experience in mathematical modeling and computation.
%We will incorporate research into teaching, especially in differential
%equation and programming courses. PI YNY will work on simple modeling of
%self-assembly problems with both undergraduate and high school students
%from Newark Science Park High School. PI YNY has a track record of
%working with local high school students for their research projects
%before they apply for colleges. PI BQ will work with undergraduate and
%high school students through the Undergraduate Research Opportunity
%Program and Young Scholar's Program as he has done in the past.

@@

\section{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena
with less computational cost than molecular dynamics, and account for
more general features that continuum theory misses. The main ingredient
is defining a nonlocal interaction through the solution of an elliptic
boundary value problem that has the phenomenological characteristics of
long-range hydrophobic attraction. It turns out that this minimal model
gives rise to rich phenomena for Janus particle aggregates and correctly
predicts elastic properties of bilayer. The technical research tasks
include quantifying collective properties of amphiphilic ensembles,
improving on mathematical models, 
efficient, high-order numerical algorithms for large-scale simulations,
and incorporating external fields through electric charge.
%Lastly, the
%proposal extends the results using three-dimensional boundary integral
%formulations.

>>>>

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles. The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science. These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes. The models describing colloidal systems could be transformative in biomedicine and material science. The research draws from expertise in scientific computing, physics of fluids, and mathematics. The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science. The project brings socially consequential research into the classroom and offers 
undergraduates the opportunity to train alongside faculty and graduate students. With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.

%The proposed mathematical analysis, modeling, and numerical algorithms
%will transform our understanding of the collective dynamics of
%amphiphilic particles such as (1) their self-assembly into micelles and
%bilayers, (2) the material properties of such self-assembly, and (3) the
%interaction between these building blocks. In addition to biophysical
%applications, amphiphilic Janus particles have recent popularity in the
%fabrication of smart materials. The proposed work will have a
%transformative impact on precision design for specific mechanical
%properties of materials made of amphiphilic nanoparticles. An important
%component of this proposal is the interdisciplinary education and
%training of both undergraduate students, graduate students, and
%postdoctoral fellows. The combination of mathematical modeling,
%analysis, and scientific computing in this project provides a compelling
%example of the importance of mathematics and computation in biophysics
%and engineering applications. The concepts and methods described here go
%beyond the context of amphiphilic particles and lipid molecules. They
%extend to other problems featuring microscopic phase separation that
%leads to formation of mesoscopic domains. This situation arises, for
%example, in biological development in systems biology. The methods
%developed here have the potential to impact those and other related
%areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
%The topics of this proposal have application in robotics, machine
%learning, and engineering.
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers (URs) per year
from the lead institution.
PI RR has worked side-by-side and
published with undergraduate coauthors in
\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}.
He is presently mentoring a Clare Boothe Luce Scholar 
on mathematical analysis of trends in election redistricting.
With another Fordham supported UR,
he is finishing a paper on a closed-form 
energy density for translationally invariant bilayers. 
Based on these experiences, we have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
%\noitemsep
\item Translate project code from MATLAB into a compiled language

@@

\end{enumerate}
The UR support is for eight summer weeks. 
In addition to collaborating with the PI,
they will have tutorials and receive training in
mathematical writing and presentation.
The URs will have desks and meeting room
in a recently completed collaboration space
built for the Mathematics Department. 
As a condition of support, 
they will be required to write a summary report and
give a presentation in the university's undergraduate
research symposium.  The PI 
will encourage the
URs to participate in a national conference.

@@

To maximize vertical integration, the PIs and personnel
will travel to New York for one or two weeks during the summers.
Finally, we will create several modules to include in our courses. These
modules will introduce topics from numerical linear algebra and
optimization and highlight concrete applications of mathematics
based on the ideas of the proposal.
%The proposed research will have an immediate impact on undergraduate and
%graduate education. At the undergraduate level, the project will include
%and support undergraduate researchers from Fordham University. The
%supported summer researchers will gain valuable first-hand
%interdisciplinary experience in mathematical modeling and computation.
%We will incorporate research into teaching, especially in differential
%equation and programming courses. PI YNY will work on simple modeling of
%self-assembly problems with both undergraduate and high school students
%from Newark Science Park High School. PI YNY has a track record of
%working with local high school students for their research projects
%before they apply for colleges. PI BQ will work with undergraduate and
%high school students through the Undergraduate Research Opportunity
%Program and Young Scholar's Program as he has done in the past.

@@

\section{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses. The main ingredient is defining a nonlocal interaction through the solution of an elliptic boundary value problem that has the phenomenological characteristics of long-range hydrophobic attraction. This minimal model, while intuitive, is quite a general description of amphiphiles in solvent and gives rise to rich phenomena from Janus particle aggregates to correctly predicting elastic properties of bilayer. The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.
%Lastly, the
%proposal extends the results using three-dimensional boundary integral
%formulations.

### 2022-09-27 NSF2022/Description/specificaim1.tex

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
 \caption{\label{fig:flow_map}
   In the HAP formulation,
   a system of exterior problems 
   defines the hydronamic and hydrophobic interactions.
   The colormap is for the intensity of $u$.
   The dynamics lead to self-organized structures like a vesicle bilayer.}
\end{wrapfigure}

@@

\begin{wrapfigure}[10]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/3Particles.jpg}
 \caption{\label{fig:3particles}
   \footnotesize
   Particles translate and rotate to lower the free energy $F[u]$
   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
   The arrows are the velocity field $\mathbf{u}$.
 }
\end{wrapfigure}
The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

@@

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}
Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[13]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, long time.
  }
\end{wrapfigure}
Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

@@

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control surface properties independently, 
which can be difficult to accomplish experimentaly 
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density function for 
relative orientation of adjacent particles
for the three boundary condition cases:
(a) is unimodal with a peak at $\theta = 0$,
(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
This kind of information can be used as an indicator
of the collective morphology. As another example,
it is costly or difficult to manufacture
Janus particles with uniform shape.
Thus, we can replace the idealistic boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function is asymptotic to a normal distribution with variance
like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example.
%\hl{Collaboration with experimental groups will
%use numerical methods to predict parameter regimes 
%to control particle-particle interactions.}

%\begin{wrapfigure}[14]{l}{0.5\textwidth}
%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
%\caption{\label{fig:multilamelar}
%  Experimentalists can transform unilamellar vesicles to% multilamellar
%  vesicles by altering the quality of the solvent
%    \cite{deMeetal21}.
%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
%  $f(u)$ and boundary conditions. 
%}
%\end{wrapfigure}

>>>>

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/Domain.jpg}
 \caption{\label{fig:flow_map}
   In the HAP formulation,
   a system of exterior problems 
   defines the hydronamic and hydrophobic interactions.
   The colormap is for the intensity of $u$.
   The dynamics lead to self-organized structures like a vesicle bilayer.}
\end{wrapfigure}

@@

\begin{wrapfigure}[10]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/3Particles.jpg}
 \caption{\label{fig:3particles}
   \footnotesize
   Particles translate and rotate to lower the free energy $F[u]$
   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
   The arrows are the velocity field $\mathbf{u}$.
 }
\end{wrapfigure}
The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

@@

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}
Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[13]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, long time.
  }
\end{wrapfigure}
Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

@@

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control surface properties independently, 
which can be difficult to accomplish experimentaly 
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density function for 
relative orientation of adjacent particles
for the three boundary condition cases:
(a) is unimodal with a peak at $\theta = 0$,
(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
This kind of information can be used as an indicator
of the collective morphology. As another example,
it is costly or difficult to manufacture
Janus particles with uniform shape.
Thus, we can replace the idealistic boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function is asymptotic to a normal distribution with variance
like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example.
